Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
minor change

A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically stable
\textit{iff} all the roots of the characteristic polynomial (i.e., the
eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
circle in the complex plane, i.e., \textit{iff} their absolute values are
less than one~\cite{astrom1997computer}.  In this paper, we express the
stability specification $\phi_{stability}$ in terms of a check known as
Jury's criterion~\cite{fadali}: this is an easy algebraic formula to select
the entries of matrix $K$, so that the closed-loop dynamics are shaped as
desired.  A detailed description of this specification can be found in
Appendix~\ref{sec:appendix-stability}.

>>>>

A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically stable
\textit{iff} all the roots of the characteristic polynomial (i.e., the
eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
circle in the complex plane, i.e., \textit{iff} their absolute values are
less than one~\cite{astrom1997computer}.  In this paper, we express the
stability specification $\phi_{stability}$ in terms of a check known as
Jury's criterion~\cite{fadali}: this is an easy algebraic formula to select
the entries of matrix $K$, so that the closed-loop dynamics are shaped as
desired (see Appendix~\ref{sec:appendix-stability} for details.
